---
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: spacelab
---

Create RSE and pheno table
==========================


This code taken from the [derfinder quick start vignette](http://www.bioconductor.org/packages/devel/bioc/vignettes/derfinder/inst/doc/derfinder-quickstart.html) gets the region matrix from a set of BigWig files included in [derfinderData](http://www.bioconductor.org/packages/derfinderData)


```{r 'setup'}
## Create a RangedSummarizedExperiment from bigwig files
library('derfinder')
library('derfinderData')
library('GenomicRanges')
library('SummarizedExperiment')

## Determine the files to use and fix the names
files <- rawFiles(system.file('extdata', 'AMY', package = 'derfinderData'), samplepatt = 'bw', fileterm = NULL)
names(files) <- gsub('.bw', '', names(files))

## Load the data from disk -- On Windows you have to load data from Bam files
fullCov <- fullCoverage(files = files, chrs = 'chr21', verbose = FALSE)

## Get the region matrix of Expressed Regions (ERs)
regionMat <- regionMatrix(fullCov, cutoff = 30, L = 76, verbose = FALSE)

## Get pheno table
pheno <- subset(brainspanPheno, structure_acronym == 'AMY')
colnames(pheno) <- tolower(colnames(pheno))
pheno$sample <- names(files)
```

# Data to upload

The following code creates a count table, a __RangedSummarizedExperiment__ object, and a phenotype table to upload to [figshare](http://figshare.com).

```{r 'export'}
## Round matrix
counts <- round(regionMat$chr21$coverageMatrix)

## Create RangedSummarizedExperiment
rse <- SummarizedExperiment(assays = list('counts' = counts), colData = DataFrame(pheno), rowRanges = regionMat$chr21$regions)

## Export data
write.table(counts, file = 'counts.tsv', quote = FALSE, sep = '\t', row.names = FALSE)
write.table(pheno, file = 'pheno.tsv', quote = FALSE, sep = '\t', row.names = FALSE)
save(rse, file = 'rse.Rdata')
```


# Converting to DESeqDataSet

The following code converts the __RangedSummarizedExperiment__ into a __DESeqDataSet__ if that is what you are interested in using. You can then use [DEFormats](http://www.bioconductor.org/packages/DEFormats) if you need to.

```{r 'deseq2'}
library('DESeq2')
dse <- DESeqDataSet(rse, design = ~gender + age)
dse
```


# Reproducibility

```{r 'reproducibility'}
## Reproducibility info
proc.time()
message(Sys.time())
options(width = 120)
devtools::session_info()
```

