---
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: spacelab
---

Download from figshare
==================

The following code downloads files from a fileset in [figshare](http://figshare.com) using [rfigshare](https://github.com/ropensci/rfigshare).


First we get the information from Figshare.

```{r 'getinfo'}
library('rfigshare')

## Authenticate if needed
# fs_auth()

## Find article
load('art_id.Rdata')

## Find article info
details <- fs_details(art_id, mine = FALSE)

## Get download URLs
down_info <- fs_download(art_id)

info <- data.frame(url = down_info[, 1], 
    name = sapply(details$files, '[[', 'name'), stringsAsFactors = FALSE)
info
```

Next we can download the __RangedSummarizedExperiment__ data.

```{r 'downloadRSE'}
## Download rse file
dir.create('downloaded', showWarnings = FALSE)
download.file(info$url[info$name == 'rse.Rdata'],
    destfile = file.path('downloaded', 'rse.Rdata'))

## Load it
library('SummarizedExperiment')
load(file.path('downloaded', 'rse.Rdata'))
rse
```

We can also re-create the __RangedSummarizedExperiment__ using [derfinder](http://www.bioconductor.org/packages/derfinder).

```{r 'remakeRSE'}
## Identify bigwig files
files <- info$url[grep('bw', info$name)]
names(files) <- gsub('.bw', '', info$name[grep('bw', info$name)])

## Download files
dir.create('bigwigs', showWarnings = FALSE)
for(i in seq_len(length(files))) download.file(files[i],
    destfile = file.path('bigwigs', paste0(names(files)[i], '.bw')))


## Locate local files
library('derfinder')
bw_files <- rawFiles('bigwigs', samplepatt = 'bw', fileterm = NULL)
names(bw_files) <- gsub('.bw', '', names(bw_files))

## Re-order names in the same way that were used originally
bw_files <- bw_files[match(colData(rse)$sample, names(bw_files))]

## Load the data from disk 
fullCov <- fullCoverage(files = bw_files, chrs = 'chr21', verbose = FALSE)

## Get the region matrix of Expressed Regions (ERs)
regionMat <- regionMatrix(fullCov, cutoff = 30, L = 76, verbose = FALSE)

## Download the pheno data
download.file(info$url[info$name == 'pheno.tsv'],
    destfile = file.path('downloaded', 'pheno.tsv'))

## Load pheno data
pheno_new <- read.table(file.path('downloaded', 'pheno.tsv'), header = TRUE,
    sep = '\t', colClasses = c('factor', 'factor', 'numeric', 'character',
    'character', 'character', 'factor', 'character'))

## Make it so it matches the original pheno table
pheno_new$group <- relevel(pheno_new$group, 'fetal')
colData(rse)$lab <- droplevels(colData(rse)$lab)

## Round matrix
counts <- round(regionMat$chr21$coverageMatrix)

## Re-create RangedSummarizedExperiment
rse_new <- SummarizedExperiment(assays = list('counts' = counts),
    colData = DataFrame(pheno_new), rowRanges = regionMat$chr21$regions)

## Apparently they are not identical
identical(rse, rse_new)

## But they are when looking closer
all(c(
    identical(assays(rse)$counts, assays(rse_new)$counts),
    identical(colData(rse), colData(rse_new)),
    identical(rowData(rse), rowData(rse_new)),
    identical(colnames(rse), colnames(rse_new)),
    identical(rownames(rse), rownames(rse_new))
))

```


# Reproducibility


```{r 'cite'}
library('knitcitations')
bib <- c('data' = read.bibtex('3187663.bib'), 
    'rfigshare' = citation('rfigshare'))
```


The data for this example is available via figshare `r citep(bib[['data']])` and was downloaded using `rfigshare` `r citep(bib[['rfigshare']])`.



```{r 'bibliography', results = 'asis'}
bibliography()
```


```{r 'reproducibility'}
## Reproducibility info
proc.time()
message(Sys.time())
options(width = 120)
devtools::session_info()
```

