---
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: spacelab
---

Upload and download from Figshare
==================

```{r 'cite'}
library('knitcitations')
bib <- c('data' = read.bibtex('3187663.bib'), 
    'rfigshare' = citation('rfigshare'),
    'derfinder' = citation('derfinder')[1])
```

This is a proof of concept on how to upload BigWig files, __RangedSummarizedExperiment__ objects, count matrices and phenotype data to [figshare](http://figshare.com) using `rfigshare` `r citep(bib[['rfigshare']])`. Then download the data and reproduce the uploaded __RangedSummarizedExperiment__ that has information at the expressed regions-level as created with `derfinder` `r citep(bib[['derfinder']])`. The resulting data that was uploaded for this test is available via figshare `r citep(bib[['data']])`.


# Files

The first file is [create_data](create_data.html) [[source file](create_data.Rmd)] which has the code for creating the phenotype table, the count matrix and the __RangedSummarizedExperiment__ to be uploaded.

Once the files have been created, [upload](upload.html) [[source file](upload.Rmd)] uploads them to [figshare](http://figshare.com) using `rfigshare`. It uploads them as a _fileset_ which means that the files will be grouped. At the end, it publishes the files so they'll be publicly available.

Finally, [download](download.html) [[source file](download.Rmd)] downloads the files and shows how to reproduce the __RangedSummarizedExperiment__ object.

# Reproducibility

```{r 'bibliography', results = 'asis'}
bibliography()
```


```{r 'reproducibility'}
## Reproducibility info
proc.time()
message(Sys.time())
options(width = 120)
devtools::session_info()
```